%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {National Renewable Energy Laboratory}{Oct 2019 -- Present}
    {Research Engineer}{Golden, CO}
    \resumeItemListStart
        \resumeItem{Leading a cross-functional team in developing and deploying a full stack web application to serve AI models to internal users. }
        \resumeItem{Leading a small team of software engineering and technicians to develop deep neural network models for the application of biomass fast characterization. (Pytorch, TensorFlow)}
        \resumeItem{Leading the development and implementation of physics based models to perform predictive simulation of various advanced biochemical processes in the biofuel industry.}
    \resumeItemListEnd
    
    \resumeSubheading
    {The University of Alabama High Performance Computing (UAHPC) group}{Aug 2018 -- Dec 2018}
    {Student Assistant (system admin)}{Tuscaloosa, AL}
    \resumeItemListStart
        \resumeItem{Worked as a system admin to assist the daily management, troubleshooting, user training for our high performance computer clusters.}
        \resumeItem{Assisted major upgrade of the system of the UAHPC with testing and fixing breaking changes, software migration issues.}
        \resumeItem{Performed GPU integration test and performance boosting benchmarks of various computational workflows including machine learning, computational fluid dynamics, molecular dynamics.}
    \resumeItemListEnd

    \resumeSubheading
    {The University of Alabama}{Aug 2014 -- Aug 2018}
    {Research Assistant}{Tuscaloosa, AL}
    \resumeItemListStart
        \resumeItem{Developed multi-physics model (C programming language) to simulate a thermal plasma reactor for the greener processing of silicon carbide.}
        \resumeItem{Developed in-house computational code (C++) for the simulation of hydrogen fuel cells.}
        \resumeItem{Developed protocols for the safe operation, maintenance, and product analysis of the thermal plasma reactor system.}
    \resumeItemListEnd

\resumeSubHeadingListEnd