%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Photographic Feedstock Material Attribute Quantification Enabled by Machine Learning (Principle Investigator)} \\
     \emph{Pytorch, TensorFlow, Flask, Vue.js, MongoDB, CI/CD, DevOps, MLOps}}    {}
    \resumeItemListStart
        \resumeItem {Leading the effort in developing machine learning based models for fast material characterization technology.}
        \resumeItem{DevOps: Developed and deployed a full-stack collaborative webapp to achieve semi-automatic image annotation.}
        \resumeItem{MLOps: Developed and implemented software framework for the machine learning model training, testing, and hyper-parameter optimization work flow.}
        \resumeItem{Achieved over 80\% accuracy for the material attribute prediction from images which is currently not possible using any other technology.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Preprocessed Feedstock Bulk Transport Phenomena Modeling} \\
     \emph{C++, Python, TensorFlow, Sci-kit Learn, SQL}}    {}
    \resumeItemListStart
        \resumeItem {Led the effort in developing hybrid neural network and physics based model to predict fixed bed chemical reactor system performance.}
        \resumeItem{Developed neural network model to predict bulk material properties from Gigabytes of data per feedstock.}
        \resumeItem{Developed physics based model to take neural network model output in predicting process performance which is validated against experiment results.}
        \resumeItem{The model developed identified risks in the scale up process for pilot scale operation and offered recommendations for reliable operation parameters.}
    \resumeItemListEnd

     \resumeProjectHeading
    {\textbf{Continuum Modeling for Feedstock-handling Equipment Design and Optimization}\\
    \emph{Python, C++}}{}
    \resumeItemListStart
        \resumeItem{Implemented material point method based solver in C++ for simulation of bulk particulate flow behavior using AMReX framework (an opensource C++ CFD framework).}
        \resumeItem{Derived mathematical formulation of material constitutive equations for bulk biomass particulate flow behavior modelling}
        \resumeItem{Achieved over 10X in computation efficiency on CPU nodes and GPU nodes compared to Discrete Element Method solvers}
    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{Modeling Flow Behavior in a Disc-Refiner for Deacetylation and Mechanical Refining process}\\
    \emph{Python, C++, SQL}}{}
    \resumeItemListStart
        \resumeItem{Developed physics model to simulate a pilot scale disc refiner for the application of biomass to biofuel.}
        \resumeItem{Achieved over 90\% accuracy when comparing model prediction with experimental measurements.}
        \resumeItem{This model contributed to the discovery of new optimal operating parameters, which reduces the energy cost of the pilot scale system by over 50\% compared to the state-of-art.}
    \resumeItemListEnd

     \resumeProjectHeading
    {\textbf{Modeling the dynamic filtration system for techno-economic analysis}\\
    \emph{Python, C++}}{}
    \resumeItemListStart
        \resumeItem{Performed 3D model construction and physic model development for dynamic filtration system to inform techno-economic analysis.}
        \resumeItem{Developed workflow to integrate custom user functions to automate the simulation-postprocessing-prediction process.}
        \resumeItem{This model enabled high fidelity techno-economical analysis of the separation process for bio-derived chemicals in a dynamic filtration system.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Cluster analysis of 3D atomic tomography of solid state matter}\\
    \emph{Python, Qt}}{}
    \resumeItemListStart
        \resumeItem{Developed an open sourced software package for cluster analysis using the hierarchical clustering algorithm.}
        \resumeItem{Implemented GUI user interface, utilized multi-thread processing to improve efficiency by over 10X compare to the original MatLab implementation.}
    \resumeItemListEnd
    

\resumeSubHeadingListEnd